---
title: "DA who I am"
author: "Your Full Name Here"
date: "Spring 2019"
output: html_document
---

### `r as.character(Sys.Date())`

```{r include=FALSE,echo=FALSE}
require(tidyverse)
if(!require("imager")) {install.packages("imager");require("imager")}

```

```{r echo=FALSE,out.width='100%'}
xx<-getwd()
Drive_ltr <- strtrim(xx,2)
yy <- str_glue("{Drive_ltr}\\AAA_Owner_Info\\My_photo.jpg")
my_pict <- load.image(yy)
plot(my_pict,axes=FALSE,main="Dr K")
```

# A Little Survey

Here are just a few questions so I can get to know you and so you can get practice submitting an assignment in Canvas.  For each question, insert your answer underneath. Make sure each answer is at the minimum a complete sentence with correctly spelled words and correct puncuation. Half the points in this assignment depend on your picture and name being correct!!  Be sure to put your photo in the AAA_Owner_Info folder and call it My_photo.jpg  

**Where are you now? What row are you in, front,middle or back?  Do you usually choose a similiar row in other classes? What is the computer number where you are sitting?  On a scale of 1 to 10, where 1 is a total dummy (doesn't know a mouse from a keyboard) and 10 is a complete geek (knows computer stuff in and out) How do you rate yourself?**  
 
##my answer   
  
I am in the front of class, instructors computer station. As an instructor I normally must sit in the front of the class, however there will be occasions where I will swap seats with a student and let the student present their material. Let mer see, the computer number is ___. On a scale of 1 to 10, I rate myself as maybe 8.5, I can program in fortran, (I dont know C or C++) but am familiar with R as a language.   
     


**Family and You? What name do you prefer to be called? Do you have room mates, live with relatives?  Do you have brothers or sisters? Where and when did you attend high school?  Do you currently have a job?**

##my answer   
  
   
 




**Aspirations?  What do you want to achieve in life?  What college subject do you think would be of the greatest interest to you? What degree or certificate are you trying to achieve?**

##my answer   
  
   
 




**Past adventures? Have you ever gone to foreign countries, if so which ones, if not Where might you go in the future?  Have you ever been in the military, if so which branch, if not which branch would you choose if you got drafted, and why?**

##my answer   
  
   
  




**Why are you taking Math 115? What grade do you need to attain in stats to not upset your future plans, What is your plan?**

##my answer   
  
   
 





**Getting around? How do you get to class? Are there issues that limit when you can be at the college?**

##my answer   
  
   
  




