---
title: "DA who I am"
author: "Your Full Name Here"
date: "Spring 2019"
output: html_document
---

### `r as.character(Sys.Date())`

```{r include=FALSE,echo=FALSE}
require(tidyverse)
if(!require("imager")) {install.packages("imager");require("imager")}

```

```{r echo=FALSE,out.width='100%'}
xx<-getwd()
Drive_ltr <- strtrim(xx,2)
yy <- str_glue("{Drive_ltr}\\AAA_Owner_Info\\My_photo.jpg")
my_pict <- load.image(yy)
plot(my_pict,axes=FALSE,main="Dr K")
```

# A Little Survey

Here are just a few questions so I can get to know you and so you can get practice submitting an assignment in Canvas.  For each question, insert your answer underneath. Make sure each answer is at the minimum a complete sentence with correctly spelled words and correct puncuation. Half the points in this assignment depend on your picture and name being correct!!  Be sure to put your photo in the AAA_Owner_Info folder and call it My_photo.jpg  

**Where are you now? What row are you in, front,middle or back?  Do you usually choose a similiar row in other classes? What is the computer number where you are sitting?  On a scale of 1 to 10, where 1 is a total dummy (doesn't know a mouse from a keyboard) and 10 is a complete geek (knows computer stuff in and out) How do you rate yourself?**  
 
##my answer   
  
I am in the front of class, instructors computer station. As an instructor I normally must sit in the front of the class, however there will be occasions where I will swap seats with a student and let the student present their material. Let mer see, the computer number is ___. On a scale of 1 to 10, I rate myself as maybe 8.5, I can program in fortran, (I dont know C or C++) but am familiar with R as a language.   
     


**Family and You? What name do you prefer to be called? Do you have room mates, live with relatives?  Do you have brothers or sisters? Where and when did you attend high school?  Do you currently have a job?**

##my answer   
  
 I prefer Dr K. I live at home with my wife Becky, (Becky was a professor of math here at AVC). I have a half-sister who lives in New Jersey, she just retired and now wants to travel the world. My grown children (Camille and Will) went to Palmdale HS in the 80's. 
 Camille now lives in Melborne, Australia with her husband and three grandkids and Will lives in Irvine where he has something to do with wingsuit flying.
   
I grew up in Pueblo Colorado and was in the first softmore class at the new high school at that time "Pueblo East high school". I graduated from East in 1962 and immediately after high school joined the army. After immiatetly recognizing that was a big mistake, 3 years later in March of 1965 I got a 3 months early discharge to attend college. I started at pueblo junior college for a quarter, then transferred to the university of Colorado where I graduated with honors in 1969. I went to graduate school from 1969 thru 1973 at University of Washington in Seattle, where I graduated with a PhD degree in mathematics in 1973. 
 




**Aspirations?  What do you want to achieve in life?  What college subject do you think would be of the greatest interest to you? What degree or certificate are you trying to achieve?**

##my answer   
  
At this point in my life, my goal is to achieve a class that can train students with the ability to recognize how to put togather an analysis of the three most common statistical problems that occur for statistical consultants. It has been demonstraighted in many progressive fouryear schools that this can be achieved in a one semester course. This particular course is the current point in that goal.  Right now the explosion of data has elevated the ideas of statistical inference and model building to center stage in research and science. Modern indivdualized medicine will lead a path in this endeavor as we struggle to understand individual gene sequences and what they do.  Where this will lead we can only guess, however the inevitable process of attempting to design our own evolution has already begun.  Just recently a scientist in china changed the genome of a pair of twin girls to insert a change in their DNA that makes them immune to aides.
 




**Past adventures? Have you ever gone to foreign countries, if so which ones, if not Where might you go in the future?  Have you ever been in the military, if so which branch, if not which branch would you choose if you got drafted, and why?**

##my answer   
  
The army was my first experience with foreign travel. For whatever stupid reason, I thought I was going to be a badass hero and join the special forces. When I was training to be a paratrooper in Fort Benning Georgia, the cuban missle crisis happened. Everybody except those in training got sent to Florida to prepare to invade Cuba. To make a long story short, the promises made by the recruter were not kept and I got sent to Germany to be on a mortar team instead of the special forces I signed up for. My greatest foreign adventure after the army was being sent to prison in Mexico in early 2000. That story is still on the internet, simply google "bill kitto accident". 
  




**Why are you taking Math 115? What grade do you need to attain in stats to not upset your future plans, What is your plan?**

##my answer   
  
   
 





**Getting around? How do you get to class? Are there issues that limit when you can be at the college?**

##my answer   
  
   
  




